### 2024-07-27 mixed-models.qmd
20240727 - mixed models

```{r}

```

@@

>>>>

```{r}
library("petersenlab")
library("lme4")
library("lmerTest")
library("MuMIn")
library("emmeans")
library("sjstats")
library("mgcv")
library("AICcmodavg")
library("parallel")
library("tidyverse")
```

### Specify Package Options {#sec-mixedModelsPackageOptions}

```{r}
emm_options(lmerTest.limit = 100000)
emm_options(pbkrtest.limit = 100000)
```

### Load Data {#sec-mixedModelsLoadData}

```{r}
#| eval: false
#| include: false

load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_depthCharts.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_weekly.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_seasonal.RData", fsep = ""))
```

```{r}
load(file = "./data/nfl_depthCharts.RData")
load(file = "./data/player_stats_weekly.RData")
load(file = "./data/player_stats_seasonal.RData")
```

We created the `player_stats_weekly.RData` and `player_stats_seasonal.RData` objects in @sec-calculatePlayerAge.

@@

## Fantasy Points Per Season by Position, Age, and Experience {#sec-fantasyPointsByAgeExperience}

```{r}
player_stats_seasonal_offense_subset <- player_stats_seasonal_offense %>% 
  filter(position_group %in% c("QB","RB","WR","TE"))

player_stats_seasonal_offense_subset$position[which(player_stats_seasonal_offense_subset$position == "HB")] <- "RB"

player_stats_seasonal_kicking_subset <- player_stats_seasonal_kicking %>% 
  filter(position == "K")

player_stats_seasonal_offense_subset <- bind_rows(
  player_stats_seasonal_offense_subset,
  player_stats_seasonal_kicking_subset
)

player_stats_seasonal_offense_subset$player_idFactor <- factor(player_stats_seasonal_offense_subset$player_id)
player_stats_seasonal_offense_subset$positionFactor <- factor(player_stats_seasonal_offense_subset$position)

#for(i in unique(nfl_depthCharts$season)){
#  print(i)
#  nfl_depthCharts %>%
#    filter(season == i) %>% 
#    select(week) %>% 
#    arrange(week) %>% 
#    unique() %>% 
#    pull() %>% 
#    print()
#}

seasons17week <- 2001:2020
seasons18week <- 2021:max(nfl_depthCharts$season, na.rm = TRUE)

endOfSeasonDepthCharts <- nfl_depthCharts %>% 
  filter((season %in% seasons17week & week == 18) | (season %in% seasons18week & week == 19)) # get end-of-season depth charts

qb1s <- endOfSeasonDepthCharts %>% 
  filter(position == "QB", depth_team == 1)

fb1s <- endOfSeasonDepthCharts %>% 
  filter(position == "FB", depth_team == 1)

k1s <- endOfSeasonDepthCharts %>% 
  filter(position == "K", depth_team == 1)

rb1s <- endOfSeasonDepthCharts %>% 
  filter(position == "RB", depth_team == 1)

wr1s <- endOfSeasonDepthCharts %>% 
  filter(position == "WR", depth_team == 1)

te1s <- endOfSeasonDepthCharts %>% 
  filter(position == "TE", depth_team == 1)

player_stats_seasonal_offense_subsetDepth <- player_stats_seasonal_offense_subset %>% 
  filter(player_id %in% c(
    qb1s$gsis_id,
    fb1s$gsis_id,
    k1s$gsis_id,
    rb1s$gsis_id,
    wr1s$gsis_id,
    te1s$gsis_id
    ))
```

### Plots of Raw Data {#sec-fantasyPointsByAgeExperienceRawData}

Plots of players' raw fantasy points data by age are in Figures [-@fig-rawFantasyPointsByAgeQB]–[-@fig-rawFantasyPointsByAgeTE].

```{r}
#| label: fig-rawFantasyPointsByAgeQB
#| fig-cap: "Plot of Raw Trajectories of Fantasy Points by Age for Quarterbacks."

ggplot(
  data = player_stats_seasonal_offense_subset %>% filter(position == "QB"),
  mapping = aes(
    x = age,
    y = fantasy_points,
    group = player_id)) +
  geom_line()  +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age",
    subtitle = "Quarterbacks"
  ) +
  theme_classic()
```

```{r}
#| label: fig-rawFantasyPointsByAgeFB
#| fig-cap: "Plot of Raw Trajectories of Fantasy Points by Age for Fullbacks."

ggplot(
  data = player_stats_seasonal_offense_subset %>% filter(position == "FB"),
  mapping = aes(
    x = age,
    y = fantasy_points,
    group = player_id)) +
  geom_line()  +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age",
    subtitle = "Fullbacks"
  ) +
  theme_classic()
```

```{r}
#| label: fig-rawFantasyPointsByAgeRB
#| fig-cap: "Plot of Raw Trajectories of Fantasy Points by Age for Running Backs."

ggplot(
  data = player_stats_seasonal_offense_subset %>% filter(position == "RB"),
  mapping = aes(
    x = age,
    y = fantasy_points,
    group = player_id)) +
  geom_line()  +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age",
    subtitle = "Running Backs"
  ) +
  theme_classic()
```

```{r}
#| label: fig-rawFantasyPointsByAgeWR
#| fig-cap: "Plot of Raw Trajectories of Fantasy Points by Age for Wide Receivers."

ggplot(
  data = player_stats_seasonal_offense_subset %>% filter(position == "WR"),
  mapping = aes(
    x = age,
    y = fantasy_points,
    group = player_id)) +
  geom_line()  +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age",
    subtitle = "Wide Receivers"
  ) +
  theme_classic()
```

```{r}
#| label: fig-rawFantasyPointsByAgeTE
#| fig-cap: "Plot of Raw Trajectories of Fantasy Points by Age for Tight Ends."

ggplot(
  data = player_stats_seasonal_offense_subset %>% filter(position == "TE"),
  mapping = aes(
    x = age,
    y = fantasy_points,
    group = player_id)) +
  geom_line()  +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age",
    subtitle = "Tight Ends"
  ) +
  theme_classic()
```

### Models {#sec-fantasyPointsByAgeExperienceModels}

```{r}
pointsPerSeason_nullModel <- lmerTest::lmer(
  fantasy_points ~ 1 + (1 | player_idFactor),
  data = player_stats_seasonal_offense_subset,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(pointsPerSeason_nullModel)
MuMIn::r.squaredGLMM(pointsPerSeason_nullModel)
performance::icc(pointsPerSeason_nullModel)
AIC(pointsPerSeason_nullModel)

pointsPerSeason_position <- lmerTest::lmer(
  fantasy_points ~ positionFactor + (1 | player_idFactor),
  data = player_stats_seasonal_offense_subset,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(pointsPerSeason_position)
MuMIn::r.squaredGLMM(pointsPerSeason_position)
emmeans::emmeans(pointsPerSeason_position, "positionFactor")
performance::icc(pointsPerSeason_position)
AIC(pointsPerSeason_position)

pointsPerSeason_positionAgeFixedLinearSlopes <- lmerTest::lmer(
  fantasy_points ~ positionFactor + ageCentered20 + (1 | player_idFactor),
  data = player_stats_seasonal_offense_subset,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(pointsPerSeason_positionAgeFixedLinearSlopes)
MuMIn::r.squaredGLMM(pointsPerSeason_positionAgeFixedLinearSlopes)
emmeans::emmeans(pointsPerSeason_positionAgeFixedLinearSlopes, "positionFactor")
emmeans::emmeans(pointsPerSeason_positionAgeFixedLinearSlopes, "ageCentered20")
performance::icc(pointsPerSeason_positionAgeFixedLinearSlopes)
AIC(pointsPerSeason_positionAgeFixedLinearSlopes)

pointsPerSeason_positionAgeRandomLinearSlopes <- lmerTest::lmer(
  fantasy_points ~ positionFactor + ageCentered20 + (1 + ageCentered20 | player_idFactor),
  data = player_stats_seasonal_offense_subset,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(pointsPerSeason_positionAgeRandomLinearSlopes)
MuMIn::r.squaredGLMM(pointsPerSeason_positionAgeRandomLinearSlopes)
emmeans::emmeans(pointsPerSeason_positionAgeRandomLinearSlopes, "positionFactor")
emmeans::emmeans(pointsPerSeason_positionAgeRandomLinearSlopes, "ageCentered20")
performance::icc(pointsPerSeason_positionAgeRandomLinearSlopes)
AIC(pointsPerSeason_positionAgeRandomLinearSlopes)

pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes <- lmerTest::lmer(
  fantasy_points ~ positionFactor + ageCentered20 + ageCentered20Quadratic + (1 + ageCentered20 | player_idFactor),
  data = player_stats_seasonal_offense_subset,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes)
MuMIn::r.squaredGLMM(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes)
emmeans::emmeans(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes, "positionFactor")
emmeans::emmeans(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes, "ageCentered20")
emmeans::emmeans(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes, "ageCentered20Quadratic")
performance::icc(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes)
AIC(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes)

pointsPerSeason_positionAgeRandomLinearRandomQuadraticSlopes <- lmerTest::lmer(
  fantasy_points ~ positionFactor + ageCentered20 + ageCentered20Quadratic + (1 + ageCentered20 + ageCentered20Quadratic | player_idFactor),
  data = player_stats_seasonal_offense_subset,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction <- lmerTest::lmer(
  fantasy_points ~ positionFactor + ageCentered20 + ageCentered20Quadratic + positionFactor:ageCentered20 + positionFactor:ageCentered20Quadratic + (1 + ageCentered20 | player_idFactor),
  data = player_stats_seasonal_offense_subset,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction)
MuMIn::r.squaredGLMM(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction)
emmeans::emmeans(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction, "positionFactor")
emmeans::emmeans(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction, "ageCentered20")
emmeans::emmeans(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes, "ageCentered20Quadratic")
performance::icc(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction)
AIC(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction)

pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience <- lmerTest::lmer(
  fantasy_points ~ positionFactor + ageCentered20 + ageCentered20Quadratic + positionFactor:ageCentered20 + positionFactor:ageCentered20Quadratic + years_of_experience + (1 + ageCentered20 | player_idFactor),
  data = player_stats_seasonal_offense_subset,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)
MuMIn::r.squaredGLMM(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)
emmeans::emmeans(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience, "positionFactor")
emmeans::emmeans(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience, "ageCentered20")
emmeans::emmeans(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience, "ageCentered20Quadratic")
emmeans::emmeans(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience, "years_of_experience")
performance::icc(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)
AIC(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)
```

Compare models:

```{r}
anova(
  pointsPerSeason_nullModel,
  pointsPerSeason_position
)

anova(
  pointsPerSeason_positionAgeFixedLinearSlopes,
  pointsPerSeason_positionAgeRandomLinearSlopes,
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes,
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction
)

mixedModels <- list(
  "null" = pointsPerSeason_nullModel,
  "position" = pointsPerSeason_position,
  "fixedLinear" = pointsPerSeason_positionAgeFixedLinearSlopes,
  "randomLinear" = pointsPerSeason_positionAgeRandomLinearSlopes,
  "randomLinearFixedQuadratic" = pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes,
  "randomLinearFixedQuadraticInteraction" = pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction
)

aictab(mixedModels)
```

Generalized Additive Model:

```{r}
num_cores <- detectCores()

pointsPerSeason_gam <- bam( # using bam() instead of gam() for faster estimation due to large size of data
  fantasy_points ~ positionFactor + s(ageCentered20, by = positionFactor) + years_of_experience + s(player_idFactor, ageCentered20, bs = "re"),
  data = player_stats_seasonal_offense_subset,
  nthreads = num_cores
)

pointsPerSeason_gamSummary <- summary(pointsPerSeason_gam)

pointsPerSeason_gamSummary
pointsPerSeason_gamSummary$r.sq
MuMIn::r.squaredGLMM(pointsPerSeason_gam)
AIC(pointsPerSeason_gam)
```

Players at the top of the end-of-season depth chart:

```{r}
pointsPerSeasonDepth_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience <- lmerTest::lmer(
  fantasy_points ~ positionFactor + ageCentered20 + ageCentered20Quadratic + positionFactor:ageCentered20 + positionFactor:ageCentered20Quadratic + years_of_experience + (1 + ageCentered20 | player_idFactor),
  data = player_stats_seasonal_offense_subset,
  control = lmerControl(optimizer = "bobyqa")
)

summary(pointsPerSeasonDepth_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)
MuMIn::r.squaredGLMM(pointsPerSeasonDepth_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)
emmeans::emmeans(pointsPerSeasonDepth_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience, "positionFactor")
emmeans::emmeans(pointsPerSeasonDepth_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience, "ageCentered20")
emmeans::emmeans(pointsPerSeasonDepth_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience, "ageCentered20Quadratic")
emmeans::emmeans(pointsPerSeasonDepth_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience, "years_of_experience")
performance::icc(pointsPerSeasonDepth_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)

pointsPerSeasonDepth_gam <- bam( # using bam() instead of gam() for faster estimation due to large size of data
  fantasy_points ~ positionFactor + s(ageCentered20, by = positionFactor) + years_of_experience + s(player_idFactor, ageCentered20, bs = "re"),
  data = player_stats_seasonal_offense_subsetDepth,
  nthreads = num_cores
)

pointsPerSeasonDepth_gamSummary <- summary(pointsPerSeasonDepth_gam)

pointsPerSeasonDepth_gamSummary
pointsPerSeasonDepth_gamSummary$r.sq
MuMIn::r.squaredGLMM(pointsPerSeasonDepth_gam)
AIC(pointsPerSeasonDepth_gam)
```

### Plots of Model-Implied Fantasy Points by Position and Age {#sec-fantasyPointsByAgePlots}

```{r}
# Create newdata object
pointsPerSeason_positionAge_newData <- expand.grid(
  positionFactor = factor(c("FB","QB","RB","TE","WR")), #,"K"
  age = seq(from = 20, to = 40, length.out = 10000)
)

pointsPerSeason_positionAge_newData$ageCentered20 <- pointsPerSeason_positionAge_newData$age - 20
pointsPerSeason_positionAge_newData$ageCentered20Quadratic <- pointsPerSeason_positionAge_newData$ageCentered20 ^ 2
pointsPerSeason_positionAge_newData$years_of_experience <- floor(pointsPerSeason_positionAge_newData$ageCentered20)

# From Quadratic Model: All Players
pointsPerSeason_positionAge_newData$fantasyPoints_quadratic <- predict(
  object = pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience,
  newdata = pointsPerSeason_positionAge_newData,
  re.form = NA
)

# From Quadratic Model: Players at Top of End-of-Season Depth Chart
pointsPerSeason_positionAge_newData$fantasyPoints_depthQuadratic <- predict(
  object = pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience,
  newdata = pointsPerSeason_positionAge_newData,
  re.form = NA
)

# From GAM Model: All Players
pointsPerSeason_positionAge_newData$fantasyPoints_gam <- predict(
  object = pointsPerSeason_gam,
  newdata = pointsPerSeason_positionAge_newData,
  newdata.guaranteed = TRUE,
  exclude = "s(player_idFactor,ageCentered20)"
)

# From GAM Model: Players at Top of End-of-Season Depth Chart
pointsPerSeason_positionAge_newData$fantasyPoints_depthGAM <- predict(
  object = pointsPerSeasonDepth_gam,
  newdata = pointsPerSeason_positionAge_newData,
  newdata.guaranteed = TRUE,
  exclude = "s(player_idFactor,ageCentered20)"
)
```

Plots of model-implied fantasy points by position and age are in Figures [-@fig-fantasyPointsByAgeQuadratic]–[-@fig-fantasyPointsByAgeGAM].

```{r}
#| label: fig-fantasyPointsByAgeQuadratic
#| fig-cap: "Plot of Model-Implied Quadratic Trajectories of Fantasy Points by Age."

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_quadratic,
    color = positionFactor
  )
) + 
  geom_smooth() +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Quadratic Model with All Players"
  ) +
  theme_classic()
```

```{r}
#| label: fig-fantasyPointsByAgeQuadraticDepth
#| fig-cap: "Plot of Model-Implied Quadratic Trajectories of Fantasy Points by Age For Players Who Were Once at the Top of the End-of-Season Depth Chart."

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_depthQuadratic,
    color = positionFactor
  )
) + 
  geom_smooth() +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Quadratic Model with Players Who Were Once at Top of End-of-Season Depth Chart"
  ) +
  theme_classic()
```

```{r}
#| label: fig-fantasyPointsByAgeGAM
#| fig-cap: "Plot of Implied Trajectories of Fantasy Points by Age from a Generalized Additive Model."

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_gam,
    color = positionFactor
  )
) + 
  geom_smooth() +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Generalized Additive Model with All Players"
  ) +
  theme_classic()
```

```{r}
#| label: fig-fantasyPointsByAgeGAM
#| fig-cap: "Plot of Implied Trajectories of Fantasy Points by Age, from a Generalized Additive Model, For Players Who Were Once at the Top of the End-of-Season Depth Chart."

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_depthGAM,
    color = positionFactor
  )
) + 
  geom_smooth() +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Generalized Additive Model with Players Who Were Once at Top of End-of-Season Depth Chart"
  ) +
  theme_classic()
```

### Plots of Individuals' Model-Implied Fantasy Points by Age {#sec-fantasyPointsIndividualByAgePlots}

```{r}
player_stats_seasonal_offense_subsetCC <- player_stats_seasonal_offense_subset %>%
  filter(!is.na(player_idFactor), !is.na(fantasy_points), !is.na(positionFactor), !is.na(ageCentered20), !is.na(ageCentered20Quadratic), !is.na(years_of_experience))

player_stats_seasonal_offense_subsetCC$fantasyPoints_quadratic <- predict(
  object = pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience,
  newdata = player_stats_seasonal_offense_subsetCC
)

player_stats_seasonal_offense_subsetCC$fantasyPoints_gam <- predict(
  object = pointsPerSeason_gam,
  newdata = player_stats_seasonal_offense_subsetCC
)
```

Plots of players' model-implied fantasy points by age are in Figures [-@fig-individualFantasyPointsByAgeQB]–[-@fig-individualFantasyPointsByAgeTE].

```{r}
#| label: fig-individualFantasyPointsByAgeQB
#| fig-cap: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Generalized Additive Model, for Quarterbacks. Overlaid with the Model-Implied Trajectory for Quarterbacks."

ggplot(
  data = player_stats_seasonal_offense_subsetCC %>% filter(position == "QB"),
  mapping = aes(
    x = age,
    y = fantasyPoints_gam,
    group = player_id)) +
  geom_smooth(
    se = FALSE,
    linewidth = 0.5,
    color = "black") +
  geom_smooth(
    mapping = aes(
      x = age,
      y = fantasyPoints_gam
    ),
    data = pointsPerSeason_positionAge_newData %>% filter(positionFactor == "QB"),
    inherit.aes = FALSE,
    se = TRUE,
    linewidth = 2
  ) +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age",
    subtitle = "Quarterbacks"
  ) +
  theme_classic()
```

```{r}
#| label: fig-individualFantasyPointsByAgeFB
#| fig-cap: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Generalized Additive Model, for Fullbacks. Overlaid with the Model-Implied Trajectory for Fullbacks."

ggplot(
  data = player_stats_seasonal_offense_subsetCC %>% filter(position == "FB"),
  mapping = aes(
    x = age,
    y = fantasyPoints_gam,
    group = player_id)) +
  geom_smooth(
    se = FALSE,
    linewidth = 0.5,
    color = "black") +
  geom_smooth(
    mapping = aes(
      x = age,
      y = fantasyPoints_gam
    ),
    data = pointsPerSeason_positionAge_newData %>% filter(positionFactor == "FB"),
    inherit.aes = FALSE,
    se = TRUE,
    linewidth = 2
  ) +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age",
    subtitle = "Fullbacks"
  ) +
  theme_classic()
```

```{r}
#| label: fig-individualFantasyPointsByAgeRB
#| fig-cap: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Generalized Additive Model, for Running Backs. Overlaid with the Model-Implied Trajectory for Running Backs."

ggplot(
  data = player_stats_seasonal_offense_subsetCC %>% filter(position == "RB"),
  mapping = aes(
    x = age,
    y = fantasyPoints_gam,
    group = player_id)) +
  geom_smooth(
    se = FALSE,
    linewidth = 0.5,
    color = "black") +
  geom_smooth(
    mapping = aes(
      x = age,
      y = fantasyPoints_gam
    ),
    data = pointsPerSeason_positionAge_newData %>% filter(positionFactor == "RB"),
    inherit.aes = FALSE,
    se = TRUE,
    linewidth = 2
  ) +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age",
    subtitle = "Running Backs"
  ) +
  theme_classic()
```

```{r}
#| label: fig-individualFantasyPointsByAgeWR
#| fig-cap: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Generalized Additive Model, for Wide Receivers. Overlaid with the Model-Implied Trajectory for Wide Receivers."

ggplot(
  data = player_stats_seasonal_offense_subsetCC %>% filter(position == "WR"),
  mapping = aes(
    x = age,
    y = fantasyPoints_gam,
    group = player_id)) +
  geom_smooth(
    se = FALSE,
    linewidth = 0.5,
    color = "black") +
  geom_smooth(
    mapping = aes(
      x = age,
      y = fantasyPoints_gam
    ),
    data = pointsPerSeason_positionAge_newData %>% filter(positionFactor == "WR"),
    inherit.aes = FALSE,
    se = TRUE,
    linewidth = 2
  ) +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age",
    subtitle = "Wide Receivers"
  ) +
  theme_classic()
```

```{r}
#| label: fig-individualFantasyPointsByAgeTE
#| fig-cap: "Plot of Individuals' Implied Trajectories of Fantasy Points by Age, from a Generalized Additive Model, for Tight Ends. Overlaid with the Model-Implied Trajectory for Wide Tight Ends."

ggplot(
  data = player_stats_seasonal_offense_subsetCC %>% filter(position == "TE"),
  mapping = aes(
    x = age,
    y = fantasyPoints_gam,
    group = player_id)) +
  geom_smooth(
    se = FALSE,
    linewidth = 0.5,
    color = "black") +
  geom_smooth(
    mapping = aes(
      x = age,
      y = fantasyPoints_gam
    ),
    data = pointsPerSeason_positionAge_newData %>% filter(positionFactor == "TE"),
    inherit.aes = FALSE,
    se = TRUE,
    linewidth = 2
  ) +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age",
    subtitle = "Tight Ends"
  ) +
  theme_classic()
```
